Early Warning Signals and the Prosecutor's Fallacy

### 2013-06-12 inst/examples/Figure2.Rmd

`ro warning=FALSE, message=FALSE, comment=NA, tidy=FALSE, cache=TRUE, verbose=TRUE, cache.path="fallacy/" or`

@@

``` {r subsetdata, dependson="simdat" }
require(plyr)
zoom <- ddply(dat, "reps", function(X){
    tip <- min(which(X$value<threshold))
#print(tip)
    index <- max(tip-200,1):tip
    data.frame(time=X$time[index], value=X$value[index])
    })
````

@@

>>>>

`ro warning=FALSE, message=FALSE, comment=NA, tidy=FALSE, cache=TRUE, verbose=TRUE, cache.path="figure2/" or`

@@

``` {r subsetdata, dependson="simdat" }
require(plyr)
zoom <- ddply(dat, "reps", function(X){
    tip <- min(which(X$value<threshold))
#print(tip)
    index <- max(tip-200,1):tip
    data.frame(time=X$time[index], value=X$value[index])
    })
save(zoom, file="zoom.rda")
````

@@

``` {r save_final_data}
write.csv(dat, file="Figure2_dat.csv")
write.csv(nulldat, file="Figure2_nulldat.csv")
```
